---
title: "Replication of the Multi-State Model"
date: "`r Sys.Date()`"
output: 
  pdf_document:
    keep_tex: yes
---
```{r Options}
knitr::opts_chunk$set(
  echo = FALSE,
  warning = FALSE,
  message = FALSE,
  fig.align = "left",
  out.width = "100%", 
  tidy = TRUE
)
```

This script takes the prepared data (from *replication_data_prep*) and fits the multistate survival model to it. This is an attempt to replicate the outcomes from ten Broeke et al. (2022), and therefore much of the code is replicated, and should be accredited to, the authors of this paper. 

```{r Load data}
source("~/research-collaboration/quitting_ind_differences/dependencies.R")
path_to_plots <- "~/research-collaboration/quitting_ind_differences/replication_multistate/plots"
path_to_tables <- "~/research-collaboration/quitting_ind_differences/replication_multistate/tables"
dat <- readRDS(paste0(path_to_data, "/replication_clean.Rdata"))
dat <- data.table(dat)
setkeyv(dat, cols = c("created", "user_id"))
```

# Descriptives 
## Sample characteristics

```{r descriptives_N}
N <- dat[, uniqueN(user_id)]
N
```


```{r descriptives_N per grade}
N_grade <- dat[, .(N = uniqueN(user_id)), by = grade]
N_grade
write.csv(N_grade, paste0(path_to_tables, "/N_grade.csv"))

dat[, .N, by = .(grade, State)][order(grade, State)]
ggplot(data = dat[, .N, by = .(grade, State)][order(grade, State)]) +
  geom_bar(aes(x = grade, fill = factor(State), y = N), stat = "identity", position = "dodge") + 
  scale_fill_manual(values = colors[1:3]) +
  theme_minimal() +
  plot_theme

```

```{r descriptives_Gender}
dat[is.na(gender), gender := "not_specified"]
dat[, .N, by = gender]

dat[, .N, by = .(gender, State)][order(gender, State)]
ggplot(data = dat[, .N, by = .(gender, State)][order(gender, State)]) +
  geom_bar(aes(x = gender, fill = factor(State), y = N), stat = "identity", position = "dodge") + 
  scale_fill_manual(values = colors[1:3]) +
  theme_minimal() +
  plot_theme
```


```{r descriptives_N sessions}
# Number of sessions played
ggplot(dat[, .N, by = user_id], aes(x = N)) +
  geom_histogram(color = colors[2], fill = colors[2], alpha=0.5, bins = 100) +
  labs(x = "N per user",
       title = "Distribution of number of sessions played") +
  theme_minimal() +
  theme(legend.position = "right",
        plot.title = element_text(face = "bold", hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5)) + plot_theme
```

### State
```{r desriptives_State}
dat[, .N, by = .(correct_answered, State)]
ggplot(data = dat[, .N, by = .(correct_answered, State)]) +
  geom_bar(aes(x =factor(correct_answered), fill = factor(State), y = N), stat = "identity", position = "dodge") + 
  scale_fill_manual(values = colors) +
  theme_minimal() +
  plot_theme
```

### Sequential errors 
```{r descriptives_Sequential errors}
dat[error_seq_cat != "0", .N, by = .(gender, error_seq_cat)][order(gender, error_seq_cat)]
dat[error_seq_cat != "0", .N, by = .(grade, error_seq_cat)][order(grade, error_seq_cat)]
dat[error_seq_cat != "0", .N, by = .(State, error_seq_cat)][order(State, error_seq_cat)]

ggplot(data = dat[error_seq_cat != "0", .N, by = .(gender, error_seq_cat)][order(gender, error_seq_cat)]) +
  geom_bar(aes(x = gender, fill = factor(error_seq_cat), y = N), stat = "identity", position = "dodge") + 
  scale_fill_manual(values = colors) +
  theme_minimal() +
  plot_theme

ggplot(data = dat[error_seq_cat != "0", .N, by = .(grade, error_seq_cat)][order(grade, error_seq_cat)]) +
  geom_bar(aes(x = factor(grade), fill = factor(error_seq_cat), y = N), stat = "identity", position = "dodge") + 
  scale_fill_manual(values = colors) +
  theme_minimal() +
  plot_theme

ggplot(data = dat[error_seq_cat != "0", .N, by = .(State, error_seq_cat)][order(State, error_seq_cat)]) +
  geom_bar(aes(x = factor(State), fill = factor(error_seq_cat), y = N), stat = "identity", position = "dodge") + 
  scale_fill_manual(values = colors) +
  theme_minimal() +
  plot_theme
```

### Fast vs. slow Errors

```{r descriptives_Fast vs slow errors}
dat[Error_type != "AAA_No error", .N, by = .(gender, Error_type)][order(gender, Error_type)]
dat[Error_type != "AAA_No error", .N, by = .(grade, Error_type)][order(grade, Error_type)]
dat[Error_type != "AAA_No error", .N, by = .(State, Error_type)][order(State, Error_type)]

ggplot(data = dat[Error_type != "AAA_No error", .N, by = .(gender, Error_type)][order(gender, Error_type)]) +
  geom_bar(aes(x = gender, fill = factor(Error_type), y = N), stat = "identity", position = "dodge") + 
  scale_fill_manual(values = colors[1:2]) +
  theme_minimal() +
  plot_theme

ggplot(data = dat[Error_type != "AAA_No error", .N, by = .(grade, Error_type)][order(grade, Error_type)]) +
  geom_bar(aes(x = factor(grade), fill = factor(Error_type), y = N), stat = "identity", position = "dodge") + 
  scale_fill_manual(values = colors) +
  theme_minimal() +
  plot_theme

ggplot(data = dat[Error_type != "AAA_No error", .N, by = .(State, Error_type)][order(State, Error_type)]) +
  geom_bar(aes(x = factor(State), fill = factor(Error_type), y = N), stat = "identity", position = "dodge") + 
  scale_fill_manual(values = colors) +
  theme_minimal() +
  plot_theme
```

### Playing during school hours 

```{r descriptives_playing time}
dat[, .N, by = .(gender, weekend_evening)][order(gender, weekend_evening)]
dat[, .N, by = .(grade, weekend_evening)][order(grade, weekend_evening)]
dat[, .N, by = .(State, weekend_evening)][order(State, weekend_evening)]

ggplot(data = dat[, .N, by = .(gender, Error_type)][order(gender, Error_type)]) +
  geom_bar(aes(x = gender, fill = factor(Error_type), y = N), stat = "identity", position = "dodge") + 
  scale_fill_manual(values = colors) +
  theme_minimal() +
  plot_theme

ggplot(data = dat[, .N, by = .(grade, weekend_evening)][order(grade, weekend_evening)]) +
  geom_bar(aes(x = factor(grade), fill = factor(weekend_evening), y = N), stat = "identity", position = "dodge") + 
  scale_fill_manual(values = colors) +
  theme_minimal() +
  plot_theme

ggplot(data = dat[, .N, by = .(State, weekend_evening)][order(State, weekend_evening)]) +
  geom_bar(aes(x = factor(State), fill = factor(weekend_evening), y = N), stat = "identity", position = "dodge") + 
  scale_fill_manual(values = colors) +
  theme_minimal() +
  plot_theme
```


# Multistate Survial Model 
## Transition matrix

For a model with three states, a transition intensity matrix (Q) is defined:
```{r Transition matrix, echo=FALSE}
Q <- matrix(data = c(1, 1, 1, 1, 1, 1, 0, 0, 0), 
            nrow = 3,
            ncol = 3,
            byrow = T)

rownames(Q) <- colnames(Q) <- c("Persisting",
                                "Soft-Quit",
                                "Hard-Quit")

Q
```

## Model fitting

The model fit procedures are specified in a separate script, <modelfit_msm.R>. The outputs from that model fitting have been saved and can be loaded into the environment below.

<msm_constrained_all>, <msm_constrained_rt> and <msm_constrained_tz> are the constrained models. That is, the multistate models without any covariates added.

<msm_covariate_all>, <msm_covariate_rt> and <msm_covariate_tz> are the covariate models. The following covariates were added to these models:

-   Gender

-   Grade (higher grades vs. lower grades)

-   Difficulty (high vs. low, and high vs. medium)

-   Speed of errors (fast error vs. no error and slow error vs. no error)

-   Playing during vs. outside school hours

-   Sequential errors (vs. no error: 1, 2, 3, \>3)

<hr_msm_covariate_rt> and <hr_msm_covariate_tz> specify the transition probabilities for each covariate (hazard ratios) in the rekentuin and taalzee models, respectively.

```{r MSM fit, warning = FALSE, include=FALSE}
# Run this to fit the model to the data. 
# source(paste0(path, "/sepjob_msm.R"))

# Load model data
msm_constrained_all <- readRDS("~/research-collaboration/quitting_ind_differences/replication_multistate/models/msm_constrained_all.Rdata")
# msm_constrained_rt <- readRDS(paste0(path_to_data, "/msm_constrained_rt.Rdata"))
# msm_constrained_tz <- readRDS(paste0(path_to_data, "/msm_constrained_tz.Rdata"))

msm_covariate_all <- readRDS("~/research-collaboration/quitting_ind_differences/replication_multistate/models/msm_covariate_all.Rdata")
# msm_covariate_rt <- readRDS(paste0(path_to_data, "/msm_covariate_rt.Rdata"))
# msm_covariate_tz <- readRDS(paste0(path_to_data, "/msm_covariate_tz.Rdata"))

# hr_msm_covariate_all <- readRDS(paste0(path_to_data, "/hr_msm_covariate_all.Rdata"))
hr_msm_covariate_rt <- readRDS("~/research-collaboration/quitting_ind_differences/replication_multistate/models/hr_msm_covariate_rt.Rdata")
hr_msm_covariate_tz <- readRDS("~/research-collaboration/quitting_ind_differences/replication_multistate/models/hr_msm_covariate_tz.Rdata")
```


## State transition rates
### Transition intensities 
Here, the estimated Q-matrices for the constrained and covariate models are extracted.

```{r Specify model, echo=TRUE}
model <- "covariate" # "constrained" or "covariate"
```


```{r Q matrices, }
if(model == "covariate") {
  q_est <- rbind(qmatrix.msm(msm_covariate_all)[, 1], qmatrix.msm(msm_covariate_all)[, 2], qmatrix.msm(msm_covariate_all)[, 3])
} else{
   q_est <- rbind(qmatrix.msm(msm_constrained_all)[, 1], qmatrix.msm(msm_constrained_all)[, 2], qmatrix.msm(msm_constrained_all)[, 3])
}

rownames(q_est) <- c("Persisting > Persiting", 
                     "Persiting > Soft-Quit", 
                     "Persiting > Hard-Quit",
                     "Soft-Quit > Persiting", 
                     "Soft-Quit > Soft-Quit", 
                     "Soft-Quit > Hard-Quit",
                     "Hard-Quit > Persiting", 
                     "Hard-Quit > Soft-Quit", 
                     "Hard-Quit > Hard-Quit")
q_est <- as.data.frame(round(q_est[c(1:2, 4:5, 7:8),], 3))
q_est$"95% CI" <- paste("[", q_est$lower, "  ", q_est$upper, "]") 
q_est$"95% CI" <- as.character(q_est$"95% CI")
q_est <- q_est[, -c(3:4)]
q_est
if(model == "covariate") {
  write.csv(q_est, file = paste0(path_to_tables, "/q_matrix_cov.csv")) 
} else {
  write.csv(q_est, file = paste0(path_to_tables, "/q_matrix_con.csv")) 
}
```

### Transition Probabilities
Also extracting state transition probability matrices
```{r P martices }
if(model == "covariate") {
  P_matrix <- pmatrix.msm(msm_covariate_all)
  cat("Transition probabilities for covariate model\n")
  print(P_matrix)
  write.csv(round(P_matrix, 3), file = paste0(path_to_tables, "/p_matrix_cov.csv"))
} else {
  P_matrix <- pmatrix.msm(msm_constrained_all)
  cat("Transition probabilities for constrained model\n")
  print(P_matrix)
  write.csv(round(P_matrix, 3), file = paste0(path_to_tables, "/p_matrix_con.csv"))
}
```


```{r Final state transition table}
P_matrix_cov <- round(pmatrix.msm(msm_covariate_all), 3)
Q_matrix_cov <- round(msm_covariate_all$Qmatrices$baseline, 3)

p <- data.frame("State" = c("Persiting", "Soft-Quit", "Hard-Quit"),
                "Persisting_P" = c(as.numeric(P_matrix_cov)[1:3]), 
                "Soft-Quit_P" = c(as.numeric(P_matrix_cov)[4:6]),
                "Hard-Quit_P" = c(as.numeric(P_matrix_cov)[7:9]))

q <- data.frame("State" = c("Persiting", "Soft-Quit", "Hard-Quit"),
                "Persisting_Q" = c(as.numeric(Q_matrix_cov)[1:3]), 
                "Soft-Quit_Q" = c(as.numeric(Q_matrix_cov)[4:6]),
                "Hard-Quit_Q" = c(as.numeric(Q_matrix_cov)[7:9]))

transition_rates_full <- cbind(q, p[,-1])

write.csv(transition_rates_full,
       paste0(path_to_tables, "/trans_rates.csv"))
```

### Likelihood Ratio Test

```{r Model comparison}
lr_test <- lrtest(msm_constrained_all, msm_covariate_all)
lr_test$Df

model_comp <- data.frame(model = c("constrained", "covariate"),
           AIC = c(round(AIC(msm_constrained_all)), round(AIC(msm_covariate_all))),
           minus_2_loglik = c(round(msm_constrained_all$minus2loglik), round(msm_covariate_all$minus2loglik)),
           lr_test_loglik = round(lr_test$LogLik),
           lr_test_df = lr_test$`#Df`,
           lr_test_df_diff = lr_test$Df,
           lr_test_chisq = lr_test$Chisq,
           lr_test_p = lr_test$`Pr(>Chisq)`)
model_comp
write.csv(model_comp,
       paste0(path_to_tables, "/model_comp.csv"))

```
The covariate model significantly improves model fit, ($\chi^2$(44) = 1238246, _p_ < 0.001), supporting the further use of this model. 

## Hazard ratios

The effect of each covariate on the model is expressed in the form of Hazard Ratios. Specifically, they are a maximum likelihood computation of the relative effect of the covariate on the probability of a state transition.

The below code extracts the hazard ratios from the covariate model, and adds them to a table (*hazardratios*) that can be used to plot the data.

```{r Prep data for plotting, include=FALSE}
varnames_plot <- c("1 Seq error \n vs. No error",
                   "2 Seq errors \n vs. No error",
                   "3 Seq errors \n vs. No error",
                   ">3 Seq errors \n vs. No error",
                   "Fast error  \n vs. No error",
                   "Slow error  \n vs. No error",
                   "During school \n vs. Outside school",
                    "Low vs.High \n Difficulty Level",
                    "Medium vs. High \n Difficulty Level",
                   "Higer grades  \n vs. Lower grades",
                   "Girls  \n vs. Boys")

order_varnames <- rev(c("Girls  \n vs. Boys",
                    "Higer grades  \n vs. Lower grades",
                    "Low vs.High \n Difficulty Level",
                    "Medium vs. High \n Difficulty Level",
                    "Slow error  \n vs. No error",
                    "Fast error  \n vs. No error",
                    "During school \n vs. Outside school",
                    ">3 Seq errors \n vs. No error",
                    "3 Seq errors \n vs. No error",
                    "2 Seq errors \n vs. No error",
                    "1 Seq error \n vs. No error"
                                           ))
```

```{r Extract hazard ratios, }
# Rekentuin
df_rt = as.data.frame(hr_msm_covariate_rt)

df_hazardratios_rt <- data.frame("application" = "rekentuin",
                                 "varnames" = sub("\\.HR$", "", 
                                               colnames(df_rt[seq(from = 1, to = length(df_rt), by = 3)])),
                                 "varnames_plot" = varnames_plot,
                              "P-SQ_HR" = as.numeric(df_rt[1, seq(from = 1, to = length(df_rt), by = 3)]),
                              "P-SQ_CI_L" = as.numeric(df_rt[1, seq(from = 2, to = length(df_rt), by = 3)]),
                              "P-SQ_CI_U" = as.numeric(df_rt[1, seq(from = 3, to = length(df_rt), by = 3)]),
                            
                              "P-HQ_HR" = as.numeric(df_rt[2, seq(from = 1, to = length(df_rt), by = 3)]),
                              "P-HQ_CI_L" = as.numeric(df_rt[2, seq(from = 2, to = length(df_rt), by = 3)]),
                              "P-HQ_CI_U" = as.numeric(df_rt[2, seq(from = 3, to = length(df_rt), by = 3)]),
                              
                              "SQ-P_HR" = as.numeric(df_rt[3, seq(from = 1, to = length(df_rt), by = 3)]),
                              "SQ-P_CI_L" = as.numeric(df_rt[3, seq(from = 2, to = length(df_rt), by = 3)]),
                              "SQ-P_CI_U" = as.numeric(df_rt[3, seq(from = 3, to = length(df_rt), by = 3)]),
                              
                              "SQ-HQ_HR" = as.numeric(df_rt[4, seq(from = 1, to = length(df_rt), by = 3)]),
                              "SQ-HQ_CI_L" = as.numeric(df_rt[4, seq(from = 2, to = length(df_rt), by = 3)]),
                              "SQ-HQ_CI_U" = as.numeric(df_rt[4, seq(from = 3, to = length(df_rt), by = 3)])
                              )

# Append variable names
df_hazardratios_rt$varnames_plot <- factor(df_hazardratios_rt$varnames_plot,
                                           levels = order_varnames)
                                                      

# Taalzee
df_tz = as.data.frame(hr_msm_covariate_tz)

df_hazardratios_tz <- data.frame("application" = "taalzee", 
                                 "varnames" = sub("\\.HR$", "", 
                                               colnames(df_tz[seq(from = 1, to = length(df_tz), by = 3)])),
                                 "varnames_plot" = varnames_plot,
                              "P-SQ_HR" = as.numeric(df_tz[1, seq(from = 1, to = length(df_tz), by = 3)]),
                              "P-SQ_CI_L" = as.numeric(df_tz[1, seq(from = 2, to = length(df_tz), by = 3)]),
                              "P-SQ_CI_U" = as.numeric(df_tz[1, seq(from = 3, to = length(df_tz), by = 3)]),
                            
                              "P-HQ_HR" = as.numeric(df_tz[2, seq(from = 1, to = length(df_tz), by = 3)]),
                              "P-HQ_CI_L" = as.numeric(df_tz[2, seq(from = 2, to = length(df_tz), by = 3)]),
                              "P-HQ_CI_U" = as.numeric(df_tz[2, seq(from = 3, to = length(df_tz), by = 3)]),
                              
                              "SQ-P_HR" = as.numeric(df_tz[3, seq(from = 1, to = length(df_tz), by = 3)]),
                              "SQ-P_CI_L" = as.numeric(df_tz[3, seq(from = 2, to = length(df_tz), by = 3)]),
                              "SQ-P_CI_U" = as.numeric(df_tz[3, seq(from = 3, to = length(df_tz), by = 3)]),
                              
                              "SQ-HQ_HR" = as.numeric(df_tz[4, seq(from = 1, to = length(df_tz), by = 3)]),
                              "SQ-HQ_CI_L" = as.numeric(df_tz[4, seq(from = 2, to = length(df_tz), by = 3)]),
                              "SQ-HQ_CI_U" = as.numeric(df_tz[4, seq(from = 3, to = length(df_tz), by = 3)])
                              )

# Append variable names
df_hazardratios_tz$varnames_plot <- factor(df_hazardratios_tz$varnames_plot,
                                           levels = order_varnames)

# Join RT and TZ tables
hazardratios <- rbind(df_hazardratios_rt, df_hazardratios_tz)
```

### Plot

I plot the hazard ratios and their confidence intervals for the persisting \> soft-quit and persisting \> hard-quit transitions for Math Garden and Language Sea, respectively. The plot gets saved to the directory under the folder "plots".

```{r Plot HRs, fig.width = 8, fig.height = 10}
df_hr_plot <- data.frame(application = rep(c("Math Garden", "Language Sea"), each = 22),
                     transition = rep(c("Persisting to Soft-Quit" ,"Persisting to Hard-Quit"), each = 11, times = 2),
                     var = rep(factor(varnames_plot, levels = order_varnames), 4),
                     hr = c(hazardratios[hazardratios$application == "rekentuin", "P.SQ_HR"],
                            hazardratios[hazardratios$application == "rekentuin", "P.HQ_HR"],
                            hazardratios[hazardratios$application == "taalzee", "P.SQ_HR"],
                            hazardratios[hazardratios$application == "taalzee", "P.HQ_HR"]),
                     ci_l = c(hazardratios[hazardratios$application == "rekentuin", "P.SQ_CI_L"],
                            hazardratios[hazardratios$application == "rekentuin", "P.HQ_CI_L"],
                            hazardratios[hazardratios$application == "taalzee", "P.SQ_CI_L"],
                            hazardratios[hazardratios$application == "taalzee", "P.HQ_CI_L"]),
                     ci_u = c(hazardratios[hazardratios$application == "rekentuin", "P.SQ_CI_U"],
                            hazardratios[hazardratios$application == "rekentuin", "P.HQ_CI_U"],
                            hazardratios[hazardratios$application == "taalzee", "P.SQ_CI_U"],
                            hazardratios[hazardratios$application == "taalzee", "P.HQ_CI_U"])
                     )

plot_hr <- ggplot(df_hr_plot,aes(x = var, y = hr)) +
  geom_point(size = 1, color = colors[1]) + 
  geom_linerange(aes(ymin = ci_l, ymax = ci_u), 
                 color = colors[1], alpha = 0.5) + 
  geom_hline(yintercept = 1, color = colors[5], linetype = "dashed") +
  coord_flip() +
  labs(y = "Hazard Ratio", x  = "") +
  scale_y_continuous(breaks = 1:14) +
  geom_text(
    aes(x = var, y = hr, label = round(hr, 2)),
    vjust = -0.8,
    color = colors[4],
    size = 3) +
  theme_minimal() +
  theme(plot.title = element_text(face = "bold", hjust = 0.5, size = 8, color = colors[4]),
        axis.text.y = element_text(size = 8, face = "bold"),
        strip.background = element_rect(fill = colors[6], color = colors[4]),
        strip.text = element_text(color = colors[4], size = 10),
        panel.border = element_rect(color = colors[4], fill = NA, linewidth = 0.5)) +
  facet_grid(application~transition)

export_plot(plot_hr)
```


```{r Plot HRs log scale, fig.width = 8, fig.height = 10}
plot_hr_log <- plot_hr + scale_y_log10()

plot_hr_log
export_plot(plot_hr_log)
```

### Hazard ratio tables

In order to easily compare the values to the previous paper, here I extract the hazard ratios, with their confidence intervals, in table format and save them to the directory.

```{r Tables, echo=FALSE}
# Rekentuin
df_hr_plot <- as.data.table(df_hr_plot)
t_hr_sq_rt <- df_hr_plot[application == "Math Garden" & transition == "Persisting to Soft-Quit"]
t_hr_sq_rt[, "95% CI" := paste("[", round(ci_l, 3), ",", round(ci_u, 3), "]")]
t_hr_sq_rt[, hr := round(hr, 3)]
t_hr_sq_rt <- t_hr_sq_rt[,-c(5:6)]
t_hr_hq_rt <- df_hr_plot[application == "Math Garden" & transition == "Persisting to Hard-Quit"]
t_hr_hq_rt[, "95% CI" := paste("[", round(ci_l, 3), ",", round(ci_u, 3), "]")]
t_hr_hq_rt[, hr := round(hr, 3)]
t_hr_hq_rt <- t_hr_hq_rt[,-c(5:6)]
hrs_rt <- rbind(t_hr_sq_rt[, -1], t_hr_hq_rt[, -1])
colnames(hrs_rt) <- c("Transition", "Covariate", "Hazard Ratio", "95% CI")
hrs_rt

# Taalzee
df_hr_plot <- as.data.table(df_hr_plot)
t_hr_sq_tz <- df_hr_plot[application == "Language Sea" & transition == "Persisting to Soft-Quit"]
t_hr_sq_tz[, "95% CI" := paste("[", round(ci_l, 3), ",", round(ci_u, 3), "]")]
t_hr_sq_tz[, hr := round(hr, 3)]
t_hr_sq_tz <- t_hr_sq_tz[,-c(5:6)]
t_hr_hq_tz <- df_hr_plot[application == "Language Sea" & transition == "Persisting to Hard-Quit"]
t_hr_hq_tz[, "95% CI" := paste("[", round(ci_l, 3), ",", round(ci_u, 3), "]")]
t_hr_hq_tz[, hr := round(hr, 3)]
t_hr_hq_tz <- t_hr_hq_tz[,-c(5:6)]
hrs_tz <- rbind(t_hr_sq_tz[, -1], t_hr_hq_tz[, -1])
colnames(hrs_tz) <- c("Transition", "Covariate", "Hazard Ratio", "95% CI")
hrs_tz

fwrite(hrs_rt, 
       paste0(path_to_tables, "/extras/hrs_rekentuin.csv"))
fwrite(hrs_tz, 
       paste0(path_to_tables, "/extras/hrs_languagesea.csv"))
```

