---
title: "Stability of Individual Differences"
author: "Annie Johansson"
date: "`r Sys.Date()`"
output: 
  pdf_document:
    keep_tex: yes
---

This document is intended to analyze the cross-domain stability of the individual differences in error-induced quitting. I load in the glmer model results from both the addition and subtraction data, plot them side by side and correlate them. To have as large of a population pool as possible available for analysis, I collapse the testing and training datasets from the addition analysis into one. (This is also done when extracting which users to include in the glmer modeling of the subtraction data). 

```{r Set-up, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  warning = FALSE,
  message = FALSE,
  # fig.width = 8,
  # fig.height = 4,
  fig.align = "left",
  out.width = "100%", 
  tidy = TRUE
)
```

```{r Load data and models, message=FALSE, warning=FALSE}
source("~/research-collaboration/quitting_ind_differences/dependencies.R")
path_to_tables <- "~/research-collaboration/quitting_ind_differences/ind_diff_stability/tables"
path_to_tables_add_train <- "~/research-collaboration/quitting_ind_differences/ind_diff_addition/tables/train"
path_to_tables_add_test <- "~/research-collaboration/quitting_ind_differences/ind_diff_addition/tables/test"
path_to_tables_sub <- "~/research-collaboration/quitting_ind_differences/ind_diff_subtraction/tables"
path_to_plots <- "~/research-collaboration/quitting_ind_differences/ind_diff_stability/plots"

# Collapsing training and testing datasets for this analysis
dat_add_train <- readRDS(paste0("~/research-collaboration/quitting_ind_differences/data_clean/addition_train_forLMER.Rdata"))
dat_add_test <- readRDS(paste0("~/research-collaboration/quitting_ind_differences/data_clean/addition_test_forLMER.Rdata"))
dat_add <- rbind(dat_add_train, dat_add_test)
dat_add <- as.data.table(dat_add)
rm(dat_add_train, dat_add_test)

dat_sub <- readRDS(paste0(path_to_data, "/subtraction_forLMER.Rdata"))
dat_sub <- as.data.table(dat_sub)

model_add <- readRDS("~/research-collaboration/quitting_ind_differences/ind_diff_addition/models/train/ran_int_slope_cov.RData")
model_sub <- readRDS("~/research-collaboration/quitting_ind_differences/ind_diff_subtraction/models/lmer_sub.RData")
```

# Fixed effects estimates
```{r GLMER Fixed Effects Addition & Subtraction, eval = FALSE}
cat("\nSummary statistics for mixed model with a random intercept and slope with covariates:\n\n")
cat("Addition \n")
summary(model_add)$coef
cat("\nSubtraction \n")
summary(model_sub)$coef
```

```{r Plot GLMER Fixed Effects Addition & Subtraction }
# df_fe_add <- as.data.frame(FEsim(model_add))
# df_fe_add <- df_fe_add[-1,]
# df_fe_add$dat <- "Addition"
# 
# df_fe_sub <- as.data.frame(FEsim(model_sub))
# df_fe_sub <- df_fe_sub[-1,]
# df_fe_sub$dat <- "Subtraction"
# 
# df_fe <- rbind(df_fe_add, df_fe_sub)
# 
# saveRDS(df_fe, paste0(path_to_tables, "/df_fe_sim.Rdata"))
df_fe <- readRDS(paste0(path_to_tables, "/df_fe_sim.Rdata"))

df_fe$term <- factor(df_fe$term, levels = c("error_seq", "rat_center", "grade"), labels = c("Sequential Errors", "Ability Rating", "Grade"))

# Plot fixed effects 
fixed_ef <- ggplot(data = df_fe) +
  aes(x = term, ymin = mean - 1.96 * sd,
      ymax = mean + 1.96 * sd, y = mean) +
  geom_point(color = colors[1], size = pointsize) +
  geom_linerange(color = colors[1], linewidth = linesize, alpha = alpha) +
  geom_hline(yintercept = 0, color = colors[5], linetype = "dashed") +
  coord_flip() +
  plot_theme + 
  labs(title = "Fixed Effect Coefficients",
                    x = "Covariate", y = "Fixed Effect Estimate") +
  facet_wrap(~dat) +
  theme(legend.position = "none")
        # strip.background = element_rect(fill = colors[6], color = colors[4]),
        # strip.text = element_text(color = colors[4], size = 10),
        # panel.border = element_rect(color = colors[4], fill = NA, linewidth = 0.5)) +
  
fixed_ef
```

# Random effects estimates
```{r GLMER variance statistics add&sub, eval = FALSE}
cat("\nVariance estimates for mixed model with a random intercept and slope with covariates:\n\n")
stats_add <- summary(model_add)
stats_add$varcor

cat("\nVariance estimates for mixed model with a random intercept and slope with covariates:\n\n")
stats_sub <- summary(model_sub)
stats_sub$varcor
```

```{r GLMER Random Effects Addition & Subtraction, warning=FALSE, message=FALSE}
# # Make dataframe of random effects
# ranef_add <- ranef(model_add)$user_id
# ranef_add$user_id <- as.numeric(rownames(ranef_add))
# ranef_sub <- ranef(model_sub)$user_id
# ranef_sub$user_id <- as.numeric(rownames(ranef_sub))
# 
# ranef_add <- data.table(ranef_add)
# ranef_sub <- data.table(ranef_sub)
# 
# saveRDS(ranef_add, paste0(path_to_tables, "/ranef_add.Rdata"))
# saveRDS(ranef_sub, paste0(path_to_tables, "/ranef_sub.Rdata"))

ranef_add_train <- readRDS(paste0(path_to_tables_add_train, "/ranef_add.Rdata"))
ranef_add_test <- readRDS(paste0(path_to_tables_add_test, "/ranef_add.Rdata"))
ranef_add <- rbind(ranef_add_train, ranef_add_test)
ranef_sub <- readRDS(paste0(path_to_tables_sub, "/ranef_sub.Rdata"))
ranef <- rbind(ranef_add, ranef_sub)
```

## Distribution of random effects 

```{r GLMER Random Effects Addition & Subtraction2, warning=FALSE, message=FALSE}
# # Density plot, centered around zero
# df_ran_effects_cov <- data.frame(dat = c(rep("Addtion", nrow(ranef_add)*2), rep("Subtraction", nrow(ranef_sub)*2)),
#                              user_id = rep(c(ranef_add$user_id, ranef_sub$user_id), each = 2), 
#                                  effect = c(rep(c("intercept", "slope"), each = c(nrow(ranef_add))),
#                                             rep(c("intercept", "slope"), each = c(nrow(ranef_sub)))),
#                                  estimate = c(ranef_add$`(Intercept)`, ranef_add$error_seq,
#                                                   ranef_sub$`(Intercept)`, ranef_sub$error_seq),
#                              estimate_adj = c(coef(model_add)$user_id[, "error_seq"],
#                                               coef(model_sub)$user_id[, "error_seq"]))
# 
# plot_density_center <- ggplot(df_ran_effects_cov, aes(x = estimate, group = effect, color = effect, fill = effect)) +
#   geom_density(alpha = 0.1) +
#   geom_vline(xintercept = 0, linetype = "dashed", color = colors[6]) +
#   scale_discrete_manual(aesthetics = c("color", "fill"), values = colors[2:3], 
#                         name = "", labels = c("Baseline Quit Rates", "Effect of Sequential Errors on Quitting")) +
#   labs(title = "Distribution of Random Slopes and Intercepts per User",
#        x = "Estimate", y = "Density") +
#   theme_minimal() + plot_theme +
#   theme(panel.grid.major.x = element_blank(),
#         legend.position = "bottom",
#         strip.background = element_rect(fill = colors[6], color = colors[4]),
#         strip.text = element_text(color = colors[4], size = 10),
#         panel.border = element_rect(color = colors[4], fill = NA, linewidth = 0.5)) +
#   facet_wrap(~dat)
# plot_density_center

# # Fixed effect estimates 
fe_add_int <- as.numeric(fixef(model_add)[1])
fe_add_se <- as.numeric(fixef(model_add)[2])
fe_sub_int <- as.numeric(fixef(model_sub)[1])
fe_sub_se <- as.numeric(fixef(model_sub)[2])

# Density plot, adjusted for fixed effect estimates
plot_density <- ggplot(ranef, aes(x = estimate, group = effect, color = effect, fill = effect)) +
  geom_density(alpha = 0.1) +
  geom_vline(data = subset(ranef, dat == "Addition"), aes(xintercept = fe_add_int), 
             color = colors[2], linetype = "dashed", alpha = 0.7, inherit.aes = FALSE) +
  geom_vline(data = subset(ranef, dat == "Addition"), aes(xintercept = fe_add_se), 
             color = colors[3], linetype = "dashed", alpha = 0.7, inherit.aes = FALSE) +
  geom_vline(data = subset(ranef, dat == "Subtraction"), aes(xintercept = fe_sub_int), 
             color = colors[2], linetype = "dashed", alpha = 0.7, inherit.aes = FALSE) +
  geom_vline(data = subset(ranef, dat == "Subtraction"), aes(xintercept = fe_sub_se), 
             color = colors[3], linetype = "dashed", alpha = 0.7, inherit.aes = FALSE) +
  scale_discrete_manual(aesthetics = c("color", "fill"), values = colors[2:3], 
                        name = "", labels = c("Baseline Quit Rates", "Effect of Sequential Errors on Quitting")) +
  labs(title = "Distribution of Random Slopes and Intercepts per User",
       x = "Estimate", y = "Density") +
  facet_wrap(~dat) +
  theme_minimal() + plot_theme +
  theme(panel.grid.major.x = element_blank(),
        legend.position = "bottom")
        # strip.background = element_rect(fill = colors[6], color = colors[4]),
        # strip.text = element_text(color = colors[4], size = 10),
        # panel.border = element_rect(color = colors[4], fill = NA, linewidth = 0.5)) +
 
plot_density
```

## Correlation between random effects

```{r Correlation random effects, message=FALSE}
ranef_add <- ranef_add[order(user_id)]
ranef_sub <- ranef_sub[order(user_id)]
n <- length(ranef_add[user_id %in% ranef_sub[, unique(user_id)]][, unique(user_id)])
df_cor <- data.frame(user_id = ranef_add[user_id %in% ranef_sub[, unique(user_id)]][, unique(user_id)],
                     add_int = ranef_add[user_id %in% ranef_sub[, unique(user_id)]][effect == "Intercept", estimate],
                     add_slope = ranef_add[user_id %in% ranef_sub[, unique(user_id)]][effect == "Slope", estimate],
                     sub_int = ranef_sub[effect == "Intercept", estimate],
                     sub_slope = ranef_sub[effect == "Slope", estimate]
                     )

cor <- cor.test(df_cor$add_slope, df_cor$sub_slope)
cor_int <- cor.test(df_cor$add_int, df_cor$sub_int)

cat("Correlation Random Intercepts\n")
cor_int
cat("\nCorrelation Random Slopes\n")
cor
```

```{r Plot correlation, fig.width=4, fig.height=5}
# Create a data frame for plotting
r_int <- paste("r = ", round(as.numeric(cor_int$estimate), 2))
r_slope <- paste("r = ", round(as.numeric(cor$estimate), 2))

df_cor_plot <- data.frame(est = rep(c("Intercept", "Slope"), each = length(df_cor$add_int)),
                     add = c(df_cor$add_int, df_cor$add_slope),
                     sub = c(df_cor$sub_int, df_cor$sub_slope))
df_cor_plot <- as.data.table(df_cor_plot)

# geom <- paste("r = ", r_slope)
plot_cor_facet <- ggplot(df_cor_plot, aes(x = add, y = sub)) +
  geom_point(color = colors[6], alpha = alpha) +
  geom_smooth(method = "lm", se = TRUE, aes(color = est, fill = est), alpha = alpha) + 
  #annotate("text", x = -.7, y = 2.8, label = r_slope, hjust = 0) +
  scale_discrete_manual(aesthetics = c("color", "fill"), values = colors[2:3]) +
  labs(title = "Correlation Between Random Effects",
       # subtitle = paste("Pearson's *r* =", round(cor$estimate, 2),
       #               "; \n *p* < .001"),
       x = "Random Effects Addition Data",
       y = "Random Effects Subtraction Data") +
  facet_wrap(~est, strip.position = "right", nrow = 2, scales = "free") +
  plot_theme +
  theme(legend.position = "none",
        panel.grid = element_blank())

plot_cor_facet
```

I use the REsim function from the package merTools to simulate the random effects from the glmer model. I do this so that I can obtain confidence intervals for plotting.
```{r Simulate Random Effects, eval=FALSE}
# Simulate confidence intervals for random effects
set.seed(1234)
ranef_add_sim <- REsim(model_add)
ranef_sub_sim <- REsim(model_sub)
ranef_add_sim$groupID <- as.numeric(ranef_add_sim$groupID)
ranef_sub_sim$groupID <- as.numeric(ranef_sub_sim$groupID)
ranef_add_sim <- data.table(ranef_add_sim)
ranef_sub_sim <- data.table(ranef_sub_sim)

# Save simulated random effects
saveRDS(ranef_add_sim, paste0(path_to_models, "/ranef_add_sim.Rdata"))
saveRDS(ranef_sub_sim, paste0(path_to_models, "/ranef_sub_sim.Rdata"))

# Load simulated random effects
ranef_add_sim <- readRDS(paste0(path_to_models, "/ranef_add_sim.Rdata"))
ranef_sub_sim <- readRDS(paste0(path_to_models, "/ranef_sub_sim.Rdata"))

# # Sample 300 users to plot
set.seed(1234)
user_ids <- sample(ranef_sub[, unique(user_id)], 300)
ranef_add_sim <- ranef_add_sim[ranef_add_sim$groupID %in% user_ids,]
ranef_sub_sim <- ranef_sub_sim[ranef_sub_sim$groupID %in% user_ids,]

# # Create dataframe of simulated random effects
p_ranef_add_sim <- plotREsim(ranef_add_sim)
p_ranef_sub_sim <- plotREsim(ranef_sub_sim)
df_ranef_add_sim <- p_ranef_add_sim$data
df_ranef_sub_sim <- p_ranef_sub_sim$data
df_ranef_add_sim$dat <- "Addition"
df_ranef_sub_sim$dat <- "Subtraction"
ranef_sim <- rbind(df_ranef_add_sim, df_ranef_sub_sim)
ranef_sim$term_label <- ifelse(ranef_sim$term == "(Intercept)", "Intercept", "Sequential Errors")
ranef_sim$user_id <- ranef_sim$groupID
user_ids <- unique(ranef_sim$groupID)
ranef_sim <- as.data.table(ranef_sim)

# # Adjust estimated effects for fixed effects
ranef_sim[term_label == "Intercept" & dat == "Addition", mean := mean + fe_add_int]
ranef_sim[term_label == "Sequential Errors" & dat == "Addition", mean := mean + fe_add_se]
ranef_sim[term_label == "Intercept" & dat == "Subtraction", mean := mean + fe_sub_int]
ranef_sim[term_label == "Sequential Errors" & dat == "Subtraction", mean := mean + fe_sub_se]

ranef_sim[term_label == "Intercept" & dat == "Addition", ymin := ymin + fe_add_int]
ranef_sim[term_label == "Sequential Errors" & dat == "Addition", ymin := ymin + fe_add_se]
ranef_sim[term_label == "Intercept" & dat == "Subtraction", ymin := ymin + fe_sub_int]
ranef_sim[term_label == "Sequential Errors" & dat == "Subtraction", ymin := ymin + fe_sub_se]

ranef_sim[term_label == "Intercept" & dat == "Addition", ymax := ymax + fe_add_int]
ranef_sim[term_label == "Sequential Errors" & dat == "Addition", ymax := ymax + fe_add_se]
ranef_sim[term_label == "Intercept" & dat == "Subtraction", ymax := ymax + fe_sub_int]
ranef_sim[term_label == "Sequential Errors" & dat == "Subtraction", ymax := ymax + fe_sub_se]

# # Combine estimated confidence intervals with coefficients from the glmer model (ranef)
ranef_subset <- ranef[user_id %in% user_ids]
ran_effects <- data.frame()
for(id in user_ids) {
  tmp <- data.frame(user_id = id,
                    dat = rep(c("Addition", "Subtraction"), each = 2),
                    effect = rep(c("Intercept", "Slope"), 2),
                    estimate = ranef_subset[user_id == id, estimate],
                    ymin = ranef_sim[user_id == id, ymin],
                    ymax = ranef_sim[user_id == id, ymax],
                    sig = ranef_sim[user_id == id, sig]
                    )
  ran_effects <- rbind(ran_effects, tmp)
}

saveRDS(ran_effects, paste0(path_to_tables, "/df_re_sim.Rdata"))
```


```{r Plot Random Effects}
ran_effects <- readRDS(paste0(path_to_tables, "/df_re_sim.Rdata"))

# # Plot random effects with CIs for the sampled users 
dataframes <- split(ran_effects, list(ran_effects$dat, ran_effects$effect))
plots <- list()
for(df in dataframes) {
  color <- ifelse(unique(df$effect) == "Slope", colors[3], colors[2])
  hline <- ifelse(unique(df$effect) == "Slope" & unique(df$dat) == "Addition",
                  fe_add_se, ifelse(unique(df$effect) == "Slope" & unique(df$dat) == "Subtraction", fe_sub_se, ifelse(unique(df$effect) == "Intercept" & unique(df$dat) == "Addition", fe_add_int, fe_sub_int)))
  ylim <- ifelse(unique(df$effect) == "Intercept", c(-7, 2), c(-1, 3))
  
  gg <- ggplot(df, aes(x = reorder(factor(user_id), estimate), y = estimate, group = dat)) +
    geom_ribbon(aes(ymin = ymin, ymax = ymax), 
                fill = color, color = NA, alpha = 0.2) +
    geom_line(color = color, linewidth = linesize, aes(alpha = sig)) +
    #geom_point(color = color, aes(alpha = sig, group = dat)) +
    # geom_linerange(aes(ymin = ymin, ymax = ymax), 
    #                color = color, linewidth = linesize, alpha = 0.05) +
    scale_alpha_manual(values = c(0.2, 0.9)) +
    geom_hline(yintercept = hline, color = color, linetype = "dashed") +
    labs(x = NULL, y = NULL) +
    plot_theme +
    theme(panel.grid.major.x = element_blank(),
          legend.position = "none",
          axis.text.x = element_blank())
          # strip.background = element_rect(fill = colors[6], color = colors[4]),
          # strip.text = element_text(color = colors[4], size = 10),
          # panel.border = element_rect(color = colors[4], fill = NA, linewidth = 0.5))
  
  ifelse(unique(df$effect) == "Intercept", 
         gg <- gg + ylim(-6, 2) + facet_wrap(~dat), 
         gg <- gg
         )
  
  ifelse(unique(df$effect) == "Intercept" & unique(df$dat) == "Subtraction", 
         gg <- gg + facet_grid(effect~dat),
         gg <- gg
         )
  
  ifelse(unique(df$effect) == "Slope" & unique(df$dat) == "Subtraction",
         gg <- gg + facet_wrap(~effect, strip.position = "right"),
         gg <- gg
         )
  
  ifelse(unique(df$effect) == "Slope",
         gg <- gg + ylim(-1, 3),
         gg <- gg
         )
  
  ifelse(unique(df$dat) == "Addition",
         gg <- gg + ylab("Effect Estimate"),
         gg <- gg
         )
  
  plots[[length(plots) + 1]] <- gg
}

grid.arrange(grobs = plots, ncol = 2, widths = c(1, 1.05))
```


```{r Plot Random Effects and Cor, fig.width=10, fig.height=6}
grid.arrange(
  arrangeGrob(
    grobs = plots,
    ncol = 2,
    widths = c(1, 1.05)
  ),
  plot_cor_facet,
  widths = c(3, 2)
)
```

### Correlation random effects with age & ability 

```{r Correlation Ability and Age - Addition}
df_add_ratgrade <- dat_add[, .(rat = unique(rat, na.rm = TRUE),
                               grade = max(grade)), by = user_id]

cat("Intercept\n\n\n")
df_add_ratgrade <- df_add_ratgrade[user_id %in% ranef_add[, unique(user_id)]]
cat("Correlation Random Intercepts Addition Game with Ability Rating:\n")
cor.test(ranef_add[order(user_id), ][effect == "Intercept", estimate], df_add_ratgrade[order(user_id), .(rat)]$rat)
cat("\n\nCorrelation Random Intercepts Addition Game with Grade:\n")
cor.test(ranef_add[order(user_id), ][effect == "Intercept", estimate], df_add_ratgrade[order(user_id), .(grade)]$grade)

cat("\n\nSlope\n\n\n")
df_add_ratgrade <- df_add_ratgrade[user_id %in% ranef_add[, unique(user_id)]]
cat("Correlation Random Effects Addition Game with Ability Rating:\n")
cor.test(ranef_add[order(user_id), ][effect == "Slope", estimate], df_add_ratgrade[order(user_id), .(rat)]$rat)
cat("\n\nCorrelation Random Effects Addition Game with Grade:\n")
cor.test(ranef_add[order(user_id), ][effect == "Slope", estimate], df_add_ratgrade[order(user_id), .(grade)]$grade)
```

```{r Correlation Ability and Age - Subtraction}
df_sub_ratgrade <- dat_sub[, .(rat = unique(user_rating, na.rm = TRUE),
                               grade = max(grade)), by = user_id]

cat("Intercept\n\n\n")
df_sub_ratgrade <- df_sub_ratgrade[user_id %in% ranef_sub[, unique(user_id)]]
cat("Correlation Random Intercepts Subtraction Game with Ability Rating:\n")
cor.test(ranef_sub[order(user_id), ][effect == "Intercept", estimate], df_sub_ratgrade[order(user_id), .(rat)]$rat)
cat("\n\nCorrelation Random Intercepts Subtraction Game with Grade:\n")
cor.test(ranef_sub[order(user_id), ][effect == "Intercept", estimate], df_sub_ratgrade[order(user_id), .(grade)]$grade)

cat("\n\nSlope\n\n\n")
df_sub_ratgrade <- df_sub_ratgrade[user_id %in% ranef_sub[, unique(user_id)]]
cat("Correlation Random Effects Subtraction Game with Ability Rating:\n")
cor.test(ranef_sub[order(user_id), ][effect == "Slope", estimate], df_sub_ratgrade[order(user_id), .(rat)]$rat)
cat("\n\nCorrelation Random Effects Subtraction Game with Grade:\n")
cor.test(ranef_sub[order(user_id), ][effect == "Slope", estimate], df_sub_ratgrade[order(user_id), .(grade)]$grade)
```

### Cross-effect correlations
To make sure that our found correlation values are meaningful and not due to a phenomenon in the data such as the positive manifold where everything is correlated with everything, I correlate the random intercepts of one domain with the random effects of the other domain. These estimates should be lower. 

```{r Cross domain correlations}
cor_crossdomain <- cor.test(df_cor$add_int, df_cor$sub_slope)
cor_crossdomain

cor_crossdomain2 <- cor.test(df_cor$add_slope, df_cor$sub_int)
cor_crossdomain2
```



